### 2019-08-11 chapters/5-experiments.tex
Add funnel with number of modules for each stage of the experiment
Add usedAsArgument and operator interactions
Finish TypeScript Declaration File Generation section

\input{figures/experiments/figExample}
\input{figures/experiments/tabAccuracy}

\section{Definitely Typed Modules}

@@

\section{JS Operators Usage}
\todo{Agregar que es una matriz simetrica. Que era para hacer un analisis mas global. Para algunos operators se puede inferir que el orden de los tipos sí afecta. Por ejemplo para instance of donde obviamente importa el orden. Pero para == por ejemplo generalmente se pone a == null y no null == a}.
\input{figures/experiments/operators/relational-operators/relationalOperators.tex}
\input{figures/experiments/operators/additive-operators/additiveOperators.tex}
\input{figures/experiments/operators/multiplicative-operators/multiplicativeOperators.tex}
\input{figures/experiments/operators/equality-operators/equalityOperators.tex}
\input{figures/experiments/operators/conditional-operators/conditionalOperators.tex}

>>>>

\input{figures/experiments/overallFunnel.tex}

\section{Definitely Typed Modules}
\todo{Poner cómo es la distribución de los tipos de declaration files.}

\draft{
module-class	503	8,27%
module	4379	71,99%
module-function	1201	19,74%
}

\draft{Chequear modulo 'acl' por ejempo que tiene errores y esta exportado como module pero deberia ser exportado como module-class. Habia otro modulo pero no lo recuerdo.}

@@

\section{JS Operators Usage} \label{sec:experiments-js-operators-usage}
\todo{Agregar que es una matriz simetrica. Que era para hacer un analisis mas global. Para algunos operators se puede inferir que el orden de los tipos sí afecta. Por ejemplo para instance of donde obviamente importa el orden. Pero para == por ejemplo generalmente se pone a == null y no null == a}.
\input{figures/experiments/operators/relational-operators/relationalOperators.tex}
\input{figures/experiments/operators/additive-operators/additiveOperators.tex}
\input{figures/experiments/operators/multiplicative-operators/multiplicativeOperators.tex}
\input{figures/experiments/operators/equality-operators/equalityOperators.tex}
\input{figures/experiments/operators/conditional-operators/conditionalOperators.tex}

### 2019-08-11 figures/approach/typescript-declaration-files-generation-method/examples/templates/module-class-template.tex
Finish TypeScript Declaration File Generation section

\begin{figure}[h]
	\centering
	\begin{lrbox}{\mintedbox}
		\begin{minipage}{0.48\textwidth}
			\jscode{code/typescript-declaration-file-generation/index.js}
		\end{minipage}
	\end{lrbox}
	\subfloat[index.js - Entry point to be executed with \mintinline{bash}{node index.js}]{\usebox{\mintedbox}}
	\hfill
	\begin{lrbox}{\mintedbox}
		\begin{minipage}{0.5\textwidth}
			\jscode{code/typescript-declaration-file-generation/calculator.js}
		\end{minipage}
	\end{lrbox}
	\subfloat[calculator.js - Module for which the TS Declaration File is going to be generated]{\usebox{\mintedbox}}

	\begin{lrbox}{\mintedbox}
		\begin{minipage}{0.7\textwidth}
			\tscode{code/typescript-declaration-file-generation/calculator.d.ts}
		\end{minipage}
	\end{lrbox}
	\subfloat[calculator/index.d.ts]{\usebox{\mintedbox}}

	\begin{lrbox}{\mintedbox}
		\begin{minipage}{0.7\textwidth}
			\tscode{code/typescript-declaration-file-generation/index.ts}
		\end{minipage}
	\end{lrbox}
	\subfloat[index.ts - TypeScript file using the generated declaration file]{\usebox{\mintedbox}}
	\caption[Declaration file generation example]{\textbf{Declaration file generation example} - Declaration file for the \mintinline{bash}{calculator} module is generated using the \mintinline{bash}{module-class.d.ts} template. Declaration file can be used within a TypeScript project: code intelligence features work as expected and the generated JavaScript file after compilation can be correctly executed.}
	\label{fig:run-time-information-gathering-get-field}
\end{figure}

>>>>

\begin{figure}[h]
	\centering
	\begin{lrbox}{\mintedbox}
		\begin{minipage}{0.48\textwidth}
			\jscode{code/typescript-declaration-file-generation/templates/module-class/index.js}
		\end{minipage}
	\end{lrbox}
	\subfloat[index.js - Entry point to be executed with \mintinline{bash}{node index.js}]{\usebox{\mintedbox}}
	\hfill
	\begin{lrbox}{\mintedbox}
		\begin{minipage}{0.5\textwidth}
			\jscode{code/typescript-declaration-file-generation/templates/module-class/calculator.js}
		\end{minipage}
	\end{lrbox}
	\subfloat[calculator.js - Module for which the TS Declaration File is going to be generated]{\usebox{\mintedbox}}

	\begin{lrbox}{\mintedbox}
		\begin{minipage}{0.7\textwidth}
			\tscode{code/typescript-declaration-file-generation/templates/module-class/calculator.d.ts}
		\end{minipage}
	\end{lrbox}
	\subfloat[calculator/index.d.ts]{\usebox{\mintedbox}}

	\begin{lrbox}{\mintedbox}
		\begin{minipage}{0.7\textwidth}
			\tscode{code/typescript-declaration-file-generation/templates/module-class/index.ts}
		\end{minipage}
	\end{lrbox}
	\subfloat[index.ts - TypeScript file using the generated declaration file]{\usebox{\mintedbox}}
	\caption[module-class.d.ts template example]{\textbf{module-class.d.ts template example} - Declaration file for the \mintinline{bash}{calculator} module is generated using the \mintinline{bash}{module-class.d.ts} template. Exported module can be used as a constructor within a TypeScript project.}
	\label{fig:ts-declaration-file-module-class-template}
\end{figure}

### 2019-08-11 figures/approach/typescript-declaration-files-generation-method/examples/templates/module-template.tex
Finish TypeScript Declaration File Generation section

\begin{figure}[h]
	\centering
	\begin{lrbox}{\mintedbox}
		\begin{minipage}{0.48\textwidth}
			\jscode{code/typescript-declaration-file-generation/templates/module-class/index.js}
		\end{minipage}
	\end{lrbox}
	\subfloat[index.js - Entry point to be executed with \mintinline{bash}{node index.js}]{\usebox{\mintedbox}}
	\hfill
	\begin{lrbox}{\mintedbox}
		\begin{minipage}{0.5\textwidth}
			\jscode{code/typescript-declaration-file-generation/templates/module-class/calculator.js}
		\end{minipage}
	\end{lrbox}
	\subfloat[calculator.js - Module for which the TS Declaration File is going to be generated]{\usebox{\mintedbox}}

	\begin{lrbox}{\mintedbox}
		\begin{minipage}{0.7\textwidth}
			\tscode{code/typescript-declaration-file-generation/templates/module-class/calculator.d.ts}
		\end{minipage}
	\end{lrbox}
	\subfloat[calculator/index.d.ts]{\usebox{\mintedbox}}

	\begin{lrbox}{\mintedbox}
		\begin{minipage}{0.7\textwidth}
			\tscode{code/typescript-declaration-file-generation/templates/module-class/index.ts}
		\end{minipage}
	\end{lrbox}
	\subfloat[index.ts - TypeScript file using the generated declaration file]{\usebox{\mintedbox}}
	\caption[module-class.d.ts template example]{\textbf{module-class.d.ts template example} - Declaration file for the \mintinline{bash}{calculator} module is generated using the \mintinline{bash}{module-class.d.ts} template. Exported module can be used as a constructor within a TypeScript project.}
	\label{fig:ts-declaration-file-module-class-template}
\end{figure}

>>>>

\begin{figure}[h]
	\centering
	\begin{lrbox}{\mintedbox}
		\begin{minipage}{0.7\textwidth}
			\jscode{code/typescript-declaration-file-generation/templates/module/index.js}
		\end{minipage}
	\end{lrbox}
	\subfloat[index.js - Entry point to be executed with \mintinline{bash}{node index.js}]{\usebox{\mintedbox}}

	\begin{lrbox}{\mintedbox}
		\begin{minipage}{0.7\textwidth}
			\jscode{code/typescript-declaration-file-generation/templates/module/calculator.js}
		\end{minipage}
	\end{lrbox}
	\subfloat[calculator.js - Module for which the TS Declaration File is going to be generated]{\usebox{\mintedbox}}

	\begin{lrbox}{\mintedbox}
		\begin{minipage}{0.9\textwidth}
			\tscode{code/typescript-declaration-file-generation/templates/module/index.d.ts}
		\end{minipage}
	\end{lrbox}
	\subfloat[calculator/index.d.ts]{\usebox{\mintedbox}}

	\caption[module.d.ts template example]{\textbf{module.d.ts template example} - Declaration file for the \mintinline{bash}{calculator} module is generated using the \mintinline{bash}{module.d.ts} template.}
	\label{fig:ts-declaration-file-module-template}
\end{figure}
